\section*{Conclusion}
\setcounter{figure}{0}
\addcontentsline{toc}{section}{Conclusion}  

This project offered us a first practical experience. Almost all of us came from preparatory classes, we had never known of such a project. It was however very complete from the exact definition with our customer until its realization. It required various technical skills such as design, automation, and programming that we did not necessarily possess at the beginning. This project was a perfect example of self-training. We learned to find answers online or to ask the right people. We were able to understand that even if we didn't know the exact answer at the beginning, we can still answer a problem.

\bigbreak
It is a very good overview of what will be our life in the professional world. We will have to combine technical skills and project management. Defining specifications, following a project, being accountable to a client, and adapting to their demands are all qualities that we have been able to develop. 

\bigbreak
The objective of the project was to design a remote-controlled robot capable of picking tomatoes. We were able to discover the difficulties that we could encounter in such a realization such as delays or lack of communication. However, we still managed to meet a large part of our customer's requests. Our robot can indeed be controlled by a user with a remote control and is able to pick up tomatoes from its plant without damaging it. Certains points non malheureusement pas pu être abordé, par exemple la mise en ligne de notre solution afin de commander ce robot à distance.

\bigbreak
Finally, from a personal point of view, this project was a real discovery for me. In my first year, I didn't know in which sector I should go. Robotics was then a great discovery and this project fascinated me. I loved the diversity of the technical tasks, but also as a project manager to face complications and look for solutions. I was also able to make contacts in the world of robotics and research which then allowed me to do an internship in research.